A Simple Minibatch Acceptance Test for MCMC

### 2016-05-18 nips_2016.tex
Shrunk two figures for Section 5.1 (Gaussians)

\begin{proof}
See Appendix~\ref{app:theory3}. {\color{blue} Daniel: Haoyu, please fix the Typos in Theorem 1
or introduce them (e.g., what is $\pi_i$?}
\end{proof}

@@

In this section, we use three experiments to reveal the benefits of our mini-batch MH testing. For
the first experiment, we illustrate that our mini-batch MH testing can obtain the posterior
distribution which is very close to the ideal one. For the second experiment, we use Logistic
regression to reveal that our mini-batch sampler is much more efficient than adaptive minibatch
approach. The third experiment shows that with the help of temperature, our mini-batch MH testing
can be used to obtain the parameters which are close to MAP.

@@

{\color{blue}
Daniel: TODO Have to show that with more data, the posterior peaks (because it is referenced by the
introduction).
}

>>>>

\begin{proof}
See Appendix~\ref{app:theory3}.
\end{proof}

@@

We conduct three sets of experiments to explore the benefits of our minibatch MH test and to
benchmark it with previous work. In Section~\ref{ssec:gaussians}, we show that our test enables
samples to converge to the posterior distribution of a Gaussian mixture model. In
Section~\ref{ssec:logistic}, we analyze the efficiency of our sampler on logistic regression. In
Section~\ref{ssec:nets}, we show that our minibatch MH can obtain good MAP estimates for deep
learning.

@@
